---
title: Data Structures
teaching: 40
exercises: 15
source: Rmd
---

::::::::::::::::::::::::::::::::::::::: objectives

- To be able to identify the 5 main data types.
- To begin exploring data frames, and understand how they are related to vectors and lists.
- To be able to ask questions from R about the type, class, and structure of an object.
- To understand the information of the attributes "names", "class", and "dim".

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: questions

- How can I read data in R?
- What are the basic data types in R?
- How do I represent categorical information in R?

::::::::::::::::::::::::::::::::::::::::::::::::::

```{r, include=FALSE}
options(stringsAsFactors = FALSE)
cats_orig <- data.frame(coat = c("calico", "black", "tabby"), weight = c(2.1, 5, 3.2), likes_string = c(1, 0, 1), stringsAsFactors = FALSE)
cats_bad <- data.frame(coat = c("calico", "black", "tabby", "tabby"), weight = c(2.1, 5, 3.2, "2.3 or 2.4"), likes_string = c(1, 0, 1, 1), stringsAsFactors = FALSE)
cats <- cats_orig
```

Rのすごい特徴のひとつは、表形式のデータ（既に手元にあるようなスプレッドシートやCSVファイル）が扱えることです。 まず、 `data/` ディレクトリに `feline-data.csv` というお試しのデータセットを作ってみましょう。

```{r}
cats <- data.frame(coat = c("calico", "black", "tabby"),
                    weight = c(2.1, 5.0, 3.2),
                    likes_string = c(1, 0, 1))
```

We can now save `cats` as a CSV file. It is good practice to call the argument
names explicitly so the function knows what default values you are changing. Here we
are setting `row.names = FALSE`. Recall you can use `?write.csv` to pull
up the help file to check out the argument names and their default values.

```{r}
write.csv(x = cats, file = "data/feline-data.csv", row.names = FALSE)
```

新しいファイル `feline-data.csv` の内容：

```{r, eval=FALSE}
coat,weight,likes_string
calico,2.1,1
black,5.0,0
tabby,3.2,1
```

:::::::::::::::::::::::::::::::::::::::::  callout

### ヒント：Rを使ったテキスト形式のファイルの編集

あるいは、テキストエディタ（Nano）またはをRStudioのメニューから File - New File - Text File を使って `data/feline-data.csv` を作成することができます。

::::::::::::::::::::::::::::::::::::::::::::::::::

以下を使って作ったデータをRへ読み込ませることができます：

```{r}
cats <- read.csv(file = "data/feline-data.csv")
cats
```

この`read.table`関数は、CSVファイル（csv = comma-separated values）のように、 データの列が区読文字で分けられたテキストファイルに収められた表形式データを 読み込むために使われます。 タブとコンマは、csvファイルでデータ点を区切る、又は分けるために使われる 最も一般的な句読文字です。
便宜上、Rでは、他に２つの`read.table`のバージョンが提供されています。 ひとつは、データがコンマで分けられているファイルのための `read.csv` 、 データがタブで分けられているファイルのための `read.delim` です。 これら３つの関数のうち、`read.csv` が最も広く使われています。  必要であれば、 `read.csv` と `read.delim`、両方の デフォルトの句読記号を置き換えることができます。

:::::::::::::::::::::::::::::::::::::::::  callout

### Check your data for factors

In recent times, the default way how R handles textual data has changed. Text
data was interpreted by R automatically into a format called "factors". But
there is an easier format that is called "character". We will hear about
factors later, and what to use them for. For now, remember that in most cases,
they are not needed and only complicate your life, which is why newer R
versions read in text as "character". Check now if your version of R has
automatically created factors and convert them to "character" format:

1. Check the data types of your input by typing `str(cats)`
2. In the output, look at the three-letter codes after the colons: If you see
   only "num" and "chr", you can continue with the lesson and skip this box.
   If you find "fct", continue to step 3.
3. Prevent R from automatically creating "factor" data. That can be done by
   the following code: `options(stringsAsFactors = FALSE)`. Then, re-read
   the cats table for the change to take effect.
4. You must set this option every time you restart R. To not forget this,
   include it in your analysis script before you read in any data, for example
   in one of the first lines.
5. For R versions greater than 4.0.0, text data is no longer converted to
   factors anymore. So you can install this or a newer version to avoid this
   problem. If you are working on an institute or company computer, ask your
   administrator to do it.

::::::::::::::::::::::::::::::::::::::::::::::::::

演算子 `$` を使って列を指定し、列を抜き出すことで、すぐにデータセットの探索を始めることができます：

```{r}
cats$weight
cats$coat
```

列に他の操作をすることもできます：

```{r}
## Say we discovered that the scale weighs two Kg light:
cats$weight + 2
paste("My cat is", cats$coat)
```

でも、こうしたらどうだろう

```{r}
cats$weight + cats$coat
```

ここで何が起こったかを理解することが、データをRでうまく分析する鍵となります。

### データ型

最後のコマンドがエラーを返すのは `2.1` 足す `"black"` はナンセンスだからだろうと思ったとしたら、 それは正解で、既にプログラミングにおける データ型 という重要な概念をある程度分かっていると言えます。 データ型が何かを知るには、以下を使います：

```{r}
typeof(cats$weight)
```

主な型は５つあります：`double（浮動小数点型）`、`integer（整数型）`、`complex（複素数型）`、`logical（論理型）`、そして`character（文字型）`。
For historic reasons, `double` is also called `numeric`.

```{r}
typeof(3.14)
typeof(1L) # The L suffix forces the number to be an integer, since by default R uses float numbers
typeof(1+1i)
typeof(TRUE)
typeof('banana')
```

どんなに分析が複雑になっても、 Rにある全てのデータは、この基本データ型のいずれかとして解釈されます。 この厳格性によって、とても重要なことが後々起こることもあります。

あるユーザーが他の猫の詳細を加えたとします。 情報は `data/feline-data_v2.csv` ファイルにあるものです。

```{r, eval=FALSE}
file.show("data/feline-data_v2.csv")
```

```{r, eval=FALSE}
coat,weight,likes_string
calico,2.1,1
black,5.0,0
tabby,3.2,1
tabby,2.3 or 2.4,1
```

先ほどのように、この新しい猫の情報を読み込み、 `weight` の列が、 どんなデータ型が確認してみましょう。

```{r}
cats <- read.csv(file="data/feline-data_v2.csv")
typeof(cats$weight)
```

なんと、この weight はdouble型ではないじゃありませんか！ 前と同じように計算をしようとすると、 やっかいなことになります：

```{r}
cats$weight + 2
```

何が起こったのでしょう？Rは、csvファイルを読み込む際、 列にある全てのものが同じ基本の型であるべきだと主張します。もし、列の 全て が、 double型であることが確認できない場合、その列の だれも double型にならないのです。
The `cats` data we are working with is something called a _data frame_. Data frames
are one of the most common and versatile types of _data structures_ we will work with in R.
A given column in a data frame cannot be composed of different data types.
In this case, R does not read everything in the data frame column `weight` as a _double_, therefore the entire
column data type changes to something that is suitable for everything in the column.

When R reads a csv file, it reads it in as a _data frame_. Thus, when we loaded the `cats`
csv file, it is stored as a data frame. We can recognize data frames by the first row that
is written by the `str()` function:

```{r}
str(cats)
```

_Data frames_ are composed of rows and columns, where each column has the
same number of rows. Different columns in a data frame can be made up of different
data types (this is what makes them so versatile), but everything in a given
column needs to be the same type (e.g., vector, factor, or list).

Let's explore more about different data structures and how they behave.
For now, let's remove that extra line from our cats data and reload it,
while we investigate this behavior further:

feline-data.csv:

```
coat,weight,likes_string
calico,2.1,1
black,5.0,0
tabby,3.2,1
```

RStudioに戻ります：

```{r, eval=FALSE}
cats <- read.csv(file="data/feline-data.csv")
```

```{r, include=FALSE}
cats <- cats_orig
```

### ベクトル及び型強制

この動作をより理解するために、もう一つのデータ構造 ベクトル を紹介します。

```{r}
my_vector <- vector(length = 3)
my_vector
```

Rのベクトルは、本来、 ベクトルの中の全てのものは同じ基本データ型でなければいけない という特別な条件のある、 順番を付けられたもののリストです。 もし、データ型を選ばなければ、デフォルトで`logical`になりますが、好きなデータ型を持つ空のベクトルを 宣言することもできます。

```{r}
another_vector <- vector(mode='character', length=3)
another_vector
```

以下を使えばベクトルかどうかを確かめられます：

```{r}
str(another_vector)
```

このコマンドから出てきた暗号みたいなアウトプットによると、このベクトルの基本データ型（ここでは `chr` （文字型））、 数（実際には、ベクトルの添字、この場合 `[1:3]` ）、 そして中身のいくつかの例示（この場合、空の文字列）が示されています。 `cats$weight`に同じようなことをすると：

```{r}
str(cats$weight)
```

ここで`cats$weight` もまたベクトルであることが分かります。 Rのデータフレームに読み込まれたデータの列は全てベクトル で、 Rが全ての列を同じ基本データ型にする理由です。

::::::::::::::::::::::::::::::::::::::  discussion

### 議論１

Why is R so opinionated about what we put in our columns of data?
How does this help us?

:::::::::::::::  solution

### 議論１

By keeping everything in a column the same, we allow ourselves to make simple
assumptions about our data; if you can interpret one entry in the column as a
number, then you can interpret _all_ of them as numbers, so we don't have to
check every time. This consistency is what people mean when they talk about
_clean data_; in the long run, strict consistency goes a long way to making
our lives easier in R.

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

#### Coercion by combining vectors

合成関数で明確な内容を持つベクトルを作ることもできます：

```{r}
combine_vector <- c(2,6,3)
combine_vector
```

これまで学んだことを踏まえて、以下は何を生み出すでしょうか。

```{r}
quiz_vector <- c(2,6,'3')
```

This is something called _type coercion_, and it is the source of many surprises
and the reason why we need to be aware of the basic data types and how R will
interpret them. When R encounters a mix of types (here double and character) to
be combined into a single vector, it will force them all to be the same
type. Consider:

```{r}
coercion_vector <- c('a', TRUE)
coercion_vector
another_coercion_vector <- c(0, TRUE)
another_coercion_vector
```

#### The type hierarchy

強制化のルールは、`logical` - `integer` - `numeric` - `complex` - `character` です。ここで、 - は、 ～が変換されるのは～ という意味です。 For
example, combining `logical` and `character` transforms the result to
`character`:

```{r}
c('a', TRUE)
```

A quick way to recognize `character` vectors is by the quotes that enclose them
when they are printed.

この流れに逆らう強制化も、`as.` 関数を使ってできます：

```{r}
character_vector_example <- c('0','2','4')
character_vector_example
character_coerced_to_double <- as.double(character_vector_example)
character_coerced_to_double
double_coerced_to_logical <- as.logical(character_coerced_to_double)
double_coerced_to_logical
```

ご覧のとおり、Rがある基本のデータ型を他へ変換すると、驚くことが起こります。 型強制の核心はさておき、ポイントは：もし、データが思っていたものと違っている場合、 型強制が原因かもしれないという事です。ベクトルの中、データフレームの列を全て同じ型にすること、 さもなくば、いやなサプライズに会う羽目になるかもしれません。

But coercion can also be very useful! For example, in our `cats` data
`likes_string` is numeric, but we know that the 1s and 0s actually represent
`TRUE` and `FALSE` (a common way of representing them). We should use the
`logical` datatype here, which has two states: `TRUE` or `FALSE`, which is
exactly what our data represents. We can 'coerce' this column to be `logical` by
using the `as.logical` function:

```{r}
cats$likes_string
cats$likes_string <- as.logical(cats$likes_string)
cats$likes_string
```

:::::::::::::::::::::::::::::::::::::::  challenge

### チャレンジ１

An important part of every data analysis is cleaning the input data. If you
know that the input data is all of the same format, (e.g. numbers), your
analysis is much easier! Clean the cat data set from the chapter about
type coercion.

#### Copy the code template

Create a new script in RStudio and copy and paste the following code. Then
move on to the tasks below, which help you to fill in the gaps (\_\_\_\_\_\_).

```
# Read data
cats <- read.csv("data/feline-data_v2.csv")

# 1. Print the data
_____

# 2. Show an overview of the table with all data types
_____(cats)

# 3. The "weight" column has the incorrect data type __________.
#    The correct data type is: ____________.

# 4. Correct the 4th weight data point with the mean of the two given values
cats$weight[4] <- 2.35
#    print the data again to see the effect
cats

# 5. Convert the weight to the right data type
cats$weight <- ______________(cats$weight)

#    Calculate the mean to test yourself
mean(cats$weight)

# If you see the correct mean value (and not NA), you did the exercise
# correctly!
```

### Instructions for the tasks

#### 1\. Print the data

Execute the first statement (`read.csv(...)`). Then print the data to the
console

:::::::::::::::  solution

### Tip 1.1

Show the content of any variable by typing its name.

### チャレンジ３の解答

Two correct solutions:

```
cats
print(cats)
```

:::::::::::::::::::::::::

#### 2\. Overview of the data types

The data type of your data is as important as the data itself. Use a
function we saw earlier to print out the data types of all columns of the
`cats` table.

:::::::::::::::  solution

### Tip 1.2

In the chapter "Data types" we saw two functions that can show data types.
One printed just a single word, the data type name. The other printed
a short form of the data type, and the first few values. We need the second
here.

:::::::::::::::::::::::::

> ### チャレンジ３の解答
>
> ```
> str(cats)
> ```

#### 3\. Which data type do we need?

The shown data type is not the right one for this data (weight of
a cat). Which data type do we need?

- Why did the `read.csv()` function not choose the correct data type?
- Fill in the gap in the comment with the correct data type for cat weight!

:::::::::::::::  solution

### Tip 1.3

Scroll up to the section about the [type hierarchy](#the-type-hierarchy)
to review the available data types

:::::::::::::::::::::::::

:::::::::::::::  solution

### チャレンジ３の解答

- Weight is expressed on a continuous scale (real numbers). The R
  data type for this is "double" (also known as "numeric").
- The fourth row has the value "2.3 or 2.4". That is not a number
  but two, and an english word. Therefore, the "character" data type
  is chosen. The whole column is now text, because all values in the same
  columns have to be the same data type.

:::::::::::::::::::::::::

#### 4\. Correct the problematic value

The code to assign a new weight value to the problematic fourth row is given.
Think first and then execute it: What will be the data type after assigning
a number like in this example?
You can check the data type after executing to see if you were right.

:::::::::::::::  solution

### Tip 1.4

Revisit the hierarchy of data types when two different data types are
combined.

:::::::::::::::::::::::::

> ### チャレンジ８の解答 1.
>
> The data type of the column "weight" is "character". The assigned data
> type is "double". Combining two data types yields the data type that is
> higher in the following hierarchy:
>
> ```
> logical < integer < double < complex < character
> ```
>
> Therefore, the column is still of type character! We need to manually
> convert it to "double".
> {: .solution}

#### 5\. Convert the column "weight" to the correct data type

Cat weight are numbers. But the column does not have this data type yet.
Coerce the column to floating point numbers.

:::::::::::::::  solution

### Tip 1.5

The functions to convert data types start with `as.`. You can look
for the function further up in the manuscript or use the RStudio
auto-complete function: Type "`as.`" and then press the TAB key.

:::::::::::::::::::::::::

> ### チャレンジ３の解答
>
> There are two functions that are synonymous for historic reasons:
>
> ```
> cats$weight <- as.double(cats$weight)
> cats$weight <- as.numeric(cats$weight)
> ```

::::::::::::::::::::::::::::::::::::::::::::::::::

### Some basic vector functions

合成関数 `c()`は、既存のベクトルに追加することもできます：

```{r}
ab_vector <- c('a', 'b')
ab_vector
combine_example <- c(ab_vector, 'SWC')
combine_example
```

数列を作ることもできます：

```{r}
mySeries <- 1:10
mySeries
seq(10)
seq(1,10, by=0.1)
```

ベクトルについて、いくつか質問することもできます：

```{r}
sequence_example <- 20:25
head(sequence_example, n=2)
tail(sequence_example, n=4)
length(sequence_example)
typeof(sequence_example)
```

We can get individual elements of a vector by using the bracket notation:

```{r}
first_element <- sequence_example[1]
first_element
```

To change a single element, use the bracket on the other side of the arrow:

```{r}
sequence_example[1] <- 30
sequence_example
```

:::::::::::::::::::::::::::::::::::::::  challenge

### チャレンジ２

Start by making a vector with the numbers 1 through 26.
Then, multiply the vector by 2.

:::::::::::::::  solution

### チャレンジ３の解答

```{r}
x <- 1:26
x <- x * 2
```

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

### リスト

覚えておきたいもう一つのデータ構造は、 `list` です。 リストは、他の種類よりも、ある意味シンプルです。その理由は、入れたいものを なんでも入れることができるからです： Remember _everything in the vector must be of the same basic data type_,
but a list can have different data types:

```{r}
list_example <- list(1, "a", TRUE, 1+4i)
list_example
```

When printing the object structure with `str()`, we see the data types of all
elements:

```{r}
str(list_example)
```

What is the use of lists? They can **organize data of different types**. For
example, you can organize different tables that belong together, similar to
spreadsheets in Excel. But there are many other uses, too.

We will see another example that will maybe surprise you in the next chapter.

To retrieve one of the elements of a list, use the **double bracket**:

```{r}
list_example[[2]]
```

The elements of lists also can have **names**, they can be given by prepending
them to the values, separated by an equals sign:

```{r}
another_list <- list(title = "Numbers", numbers = 1:10, data = TRUE )
another_list
```

This results in a **named list**. Now we have a new function of our object!
We can access single elements by an additional way!

```{r}
another_list$title
```

## Names

With names, we can give meaning to elements. It is the first time that we do not
only have the **data**, but also explaining information. It is _metadata_
that can be stuck to the object like a label. In R, this is called an
**attribute**. Some attributes enable us to do more with our
object, for example, like here, accessing an element by a self-defined name.

### Accessing vectors and lists by name

We have already seen how to generate a named list. The way to generate a named
vector is very similar. You have seen this function before:

```{r}
pizza_price <- c( pizzasubito = 5.64, pizzafresh = 6.60, callapizza = 4.50 )
```

The way to retrieve elements is different, though:

```{r}
pizza_price["pizzasubito"]
```

The approach used for the list does not work:

```{r}
pizza_price$pizzafresh
```

It will pay off if you remember this error message, you will meet it in your own
analyses. It means that you have just tried accessing an element like it was in
a list, but it is actually in a vector.

### Accessing and changing names

If you are only interested in the names, use the `names()` function:

```{r}
names(pizza_price)
```

We have seen how to access and change single elements of a vector. The same is
possible for names:

```{r}
names(pizza_price)[3]
names(pizza_price)[3] <- "call-a-pizza"
pizza_price
```

:::::::::::::::::::::::::::::::::::::::  challenge

### チャレンジ３

- What is the data type of the names of `pizza_price`? You can find out
  using the `str()` or `typeof()` functions.

:::::::::::::::  solution

### チャレンジ３の解答

You get the names of an object by wrapping the object name inside
`names(...)`. Similarly, you get the data type of the names by again
wrapping the whole code in `typeof(...)`:

```
typeof(names(pizza))
```

alternatively, use a new variable if this is easier for you to read:

```
n <- names(pizza)
typeof(n)
```

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::  challenge

### チャレンジ４

Instead of just changing some of the names a vector/list already has, you can
also set all names of an object by writing code like (replace ALL CAPS text):

```
names( OBJECT ) <-  CHARACTER_VECTOR
```

Create a vector that gives the number for each letter in the alphabet!

1. Generate a vector called `letter_no` with the sequence of numbers from 1
   to 26!
2. R has a built-in object called `LETTERS`. It is a 26-character vector, from
   A to Z. Set the names of the number sequence to this 26 letters
3. Test yourself by calling `letter_no["B"]`, which should give you the number
   2!

:::::::::::::::  solution

### チャレンジ３の解答

```
letter_no <- 1:26   # or seq(1,26)
names(letter_no) <- LETTERS
letter_no["B"]
```

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

## データフレーム

We have data frames at the very beginning of this lesson, they represent
a table of data. We didn't go much further into detail with our example cat
data frame:

```{r}
cats
```

これで、data.frameの驚くべき特徴を理解することができます。もし以下を走らせたらどうなるでしょう：

```{r}
typeof(cats)
```

We see that data.frames look like lists 'under the hood'. Think again what we
heard about what lists can be used for:

> Lists organize data of different types

Columns of a data frame are vectors of different types, that are organized
by belonging to the same table.

A data.frame is really a list of vectors. つまり、 \`\` は、全てのベクトルの長さが同じでなければならない特別なリストなのです。

How is this "special"-ness written into the object, so that R does not treat it
like any other list, but as a table?

```{r}
class(cats)
```

A **class**, just like names, is an attribute attached to the object. It tells
us what this object means for humans.

You might wonder: Why do we need another what-type-of-object-is-this-function?
We already have `typeof()`? That function tells us how the object is
**constructed in the computer**. The `class` is the **meaning of the object for
humans**. Consequently, what `typeof()` returns is _fixed_ in R (mainly the
five data types), whereas the output of `class()` is _diverse_ and _extendable_
by R packages.

我々の `cats` の例では、整数型（integer）、浮動小数型（double）、論理型（logical）の変数があります。 既に見たように、data.frame のそれぞれの列はベクトルです。

```{r}
cats$coat
cats[,1]
typeof(cats[,1])
str(cats[,1])
```

それぞれの行は、異なる変数の observation（観測値） であり、それ自体が data.frame であるため、 異なる種類の要素で構成されることができます。

```{r}
cats[1,]
typeof(cats[1,])
str(cats[1,])
```

:::::::::::::::::::::::::::::::::::::::  challenge

### チャレンジ５

There are several subtly different ways to call variables, observations and
elements from data.frames:

- `cats[1]`
- `cats[[1]]`
- `cats$coat`
- `cats["coat"]`
- `cats[1, 1]`
- `cats[, 1]`
- `cats[1, ]`

Try out these examples and explain what is returned by each one.

_Hint:_ Use the function `typeof()` to examine what is returned in each case.

:::::::::::::::  solution

### チャレンジ３の解答

```{r, eval=TRUE, echo=TRUE}
cats[1]
```

We can think of a data frame as a list of vectors. The single brace `[1]`
returns the first slice of the list, as another list. In this case it is the
first column of the data frame.

```{r, eval=TRUE, echo=TRUE}
cats[[1]]
```

The double brace `[[1]]` returns the contents of the list item. In this case
it is the contents of the first column, a _vector_ of type _character_.

```{r, eval=TRUE, echo=TRUE}
cats$coat
```

This example uses the `$` character to address items by name. _coat_ is the
first column of the data frame, again a _vector_ of type _character_.

```{r, eval=TRUE, echo=TRUE}
cats["coat"]
```

Here we are using a single brace `["coat"]` replacing the index number with
the column name. Like example 1, the returned object is a _list_.

```{r, eval=TRUE, echo=TRUE}
cats[1, 1]
```

This example uses a single brace, but this time we provide row and column
coordinates. The returned object is the value in row 1, column 1. The object
is a _vector_ of type _character_.

```{r, eval=TRUE, echo=TRUE}
cats[, 1]
```

Like the previous example we use single braces and provide row and column
coordinates. The row coordinate is not specified, R interprets this missing
value as all the elements in this _column_ and returns them as a _vector_.

```{r, eval=TRUE, echo=TRUE}
cats[1, ]
```

Again we use the single brace with row and column coordinates. The column
coordinate is not specified. The return value is a _list_ containing all the
values in the first row.

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::::  callout

### Tip: Renaming data frame columns

Data frames have column names, which can be accessed with the `names()` function.

```{r}
names(cats)
```

If you want to rename the second column of `cats`, you can assign a new name to the second element of `names(cats)`.

```{r}
names(cats)[2] <- "weight_kg"
cats
```

::::::::::::::::::::::::::::::::::::::::::::::::::

```{r, include=FALSE}
# reverting cats back to original version
cats <- cats_orig
```

### 行列

Last but not least is the matrix. We can declare a matrix full of zeros:

```{r}
matrix_example <- matrix(0, ncol=6, nrow=3)
matrix_example
```

What makes it special is the `dim()` attribute:

```{r}
dim(matrix_example)
```

そして、他のデータ構造と同様に、行列に関することを尋ねることもできます：

```{r}
typeof(matrix_example)
class(matrix_example)
str(matrix_example)
nrow(matrix_example)
ncol(matrix_example)
```

:::::::::::::::::::::::::::::::::::::::  challenge

### チャレンジ６

What do you think will be the result of
`length(matrix_example)`?
Try it.
Were you right? Why / why not?

:::::::::::::::  solution

### チャレンジ３の解答

What do you think will be the result of
`length(matrix_example)`?

```{r}
matrix_example <- matrix(0, ncol=6, nrow=3)
length(matrix_example)
```

Because a matrix is a vector with added dimension attributes, `length`
gives you the total number of elements in the matrix.

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::  challenge

### チャレンジ７

もう一つ行列を作ってみましょう、今回は、1:50の数を含むもので、 ５行、10列を持つ行列にしましょう。
この `matrix` 関数は、デフォルトでは、行か列、どちらから 行列を埋めましたか？
これがどう変化したか理解したか確認してみましょう。
(hint: read the documentation for `matrix`!)

:::::::::::::::  solution

### チャレンジ３の解答

もう一つ行列を作ってみましょう、今回は、1:50の数を含むもので、 ５行、10列を持つ行列にしましょう。
この `matrix` 関数は、デフォルトでは、行か列、どちらから 行列を埋めましたか？
これがどう変化したか理解したか確認してみましょう。
(hint: read the documentation for `matrix`!)

```{r, eval=FALSE}
x <- matrix(1:50, ncol=5, nrow=10)
x <- matrix(1:50, ncol=5, nrow=10, byrow = TRUE) # to fill by row
```

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::  challenge

### チャレンジ８

ワークショップの現パート、それぞれのセクションのために、二つの文字型ベクトルが含まれるリストを作って下さい：

- データ型
- Data structures

* データ型 - データ構造 それぞれの文字ベクトルをこれまでみてきたデータ型と データ構造で埋めてください。

:::::::::::::::  solution

### チャレンジ３の解答

```{r}
dataTypes <- c('double', 'complex', 'integer', 'character', 'logical')
dataStructures <- c('data.frame', 'vector', 'list', 'matrix')
answer <- list(dataTypes, dataStructures)
```

Note: it's nice to make a list in big writing on the board or taped to the wall
listing all of these types and structures - leave it up for the rest of the workshop
to remind people of the importance of these basics.

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::  challenge

### チャレンジ８

Consider the R output of the matrix below:

```{r, echo=FALSE}
matrix(c(4, 1, 9, 5, 10, 7), ncol = 2, byrow = TRUE)
```

この行列を書くために使ったコマンドは何でしたか？ それぞれのコマンドを確かめて、打ち込む前に正しいものが何か分かるようにしましょう。
他のコマンドでは、どのような行列が作られるかを考えてみましょう。

1. `matrix(c(4, 1, 9, 5, 10, 7), nrow = 3)`
2. `matrix(c(4, 9, 10, 1, 5, 7), ncol = 2, byrow = TRUE)`
3. `matrix(c(4, 9, 10, 1, 5, 7), nrow = 2)`
4. `matrix(c(4, 1, 9, 5, 10, 7), ncol = 2, byrow = TRUE)`

:::::::::::::::  solution

### チャレンジ３の解答

Consider the R output of the matrix below:

```{r, echo=FALSE}
matrix(c(4, 1, 9, 5, 10, 7), ncol = 2, byrow = TRUE)
```

この行列を書くために使ったコマンドは何でしたか？ それぞれのコマンドを確かめて、打ち込む前に正しいものが何か分かるようにしましょう。
他のコマンドでは、どのような行列が作られるかを考えてみましょう。

```{r, eval=FALSE}
matrix(c(4, 1, 9, 5, 10, 7), ncol = 2, byrow = TRUE)
```

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: keypoints

- Use `read.csv` to read tabular data in R.
- The basic data types in R are double, integer, complex, logical, and character.
- Data structures such as data frames or matrices are built on top of lists and vectors, with some added attributes.

::::::::::::::::::::::::::::::::::::::::::::::::::
