---
title: Exploring Data Frames
teaching: 20
exercises: 10
source: Rmd
---

::::::::::::::::::::::::::::::::::::::: objectives

- Add and remove rows or columns.
- データフレームへの追加.
- Display basic properties of data frames including size and class of the columns, names, and first few rows.

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: questions

- How can I manipulate a data frame?

::::::::::::::::::::::::::::::::::::::::::::::::::

```{r, include=FALSE}
```

At this point, you've seen it all: in the last lesson, we toured all the basic
data types and data structures in R. Everything you do will be a manipulation of
those tools. しかし大抵の場合、主役はデータフレーム（CSVファイルから情報を読み込み作成した表）です。 このレッスンでは、データフレームを使ってどう作業していくかについて更に学んでいきましょう。

## データフレームに行と列を追加する

既に学んだとおり、データフレームの列はベクトルですから、列にあるデータには一貫性があります。 ですので、新しい列を加えたい場合は、新しいベクトルを作ることから始めることになります：

```{r, echo=FALSE}
cats <- read.csv("data/feline-data.csv")
```

```{r}
age <- c(2, 3, 5)
cats
```

そして、これを以下を使って列に加えます：

```{r}
cbind(cats, age)
```

もし、データフレームの行の数と一致しない年齢のベクトルを追加しようとすると、失敗します：

```{r, error=TRUE}
age <- c(2, 3, 5, 12)
cbind(cats, age)

age <- c(2, 3)
cbind(cats, age)
```

Why didn't this work? なぜダメだったのでしょうか？もちろん、Rは新しい列のひとつの要素を、表の中にある全ての行について参照したがるものです。

```{r}
nrow(cats)
length(age)
```

So for it to work we need to have `nrow(cats)` = `length(age)`. Let's overwrite the content of cats with our new data frame.

```{r}
age <- c(2, 3, 5)
cats <- cbind(cats, age)
```

Now how about adding rows? We already know that the rows of a
data frame are lists:

```{r}
newRow <- list("tortoiseshell", 3.3, TRUE, 9)
cats <- rbind(cats, newRow)
```

Let's confirm that our new row was added correctly.

```{r}
cats
```

## 行の削除

We now know how to add rows and columns to our data frame in R. Now let's learn to remove rows.

```{r}
cats
```

この問題の行を除くようにデータフレームに頼みましょう：

```{r}
cats[-4, ]
```

コンマの後に何もないのは、４番目の行の全部を削除して欲しいということを示している点に留意しましょう。

注意：ベクトルの中に行番号を入れれば、新しく追加した行を両方削除することもできす：`cats[c(-3,-4), ]`

## 列の削除

We can also remove columns in our data frame. What if we want to remove the column "age". We can remove it in two ways, by variable number or by index.

```{r}
cats[,-4]
```

全ての行を持っていたいということを示すため、コンマの前に何も入っていない点に留意しましょう。

または、要素番号の名前を使って列を削除することもできます： The `%in%` operator goes through each element of its left argument, in this case the names of `cats`, and asks, "Does this element occur in the second argument?"

```{r}
drop <- names(cats) %in% c("age")
cats[,!drop]
```

We will cover subsetting with logical operators like `%in%` in more detail in the next episode. See the section [Subsetting through other logical operations](06-data-subsetting.Rmd)

## データフレームへの追加

データフレームにデータを加えるときに覚えておくべき重要なことは、 列はベクトルで、行はリスト であることです。 ２つのデータフレームを `rbind` を使ってくっつけることもできます：

```{r}
cats <- rbind(cats, cats)
cats
```

:::::::::::::::::::::::::::::::::::::::  challenge

## チャレンジ１

You can create a new data frame right from within R with the following syntax:

```{r}
df <- data.frame(id = c("a", "b", "c"),
                 x = 1:3,
                 y = c(TRUE, TRUE, FALSE))
```

Make a data frame that holds the following information for yourself:

- first name
- last name
- lucky number

Then use `rbind` to add an entry for the people sitting beside you.
Finally, use `cbind` to add a column with each person's answer to the question, "Is it time for coffee break?"

:::::::::::::::  solution

## チャレンジ３の解答

```{r}
df <- data.frame(first = c("Grace"),
                 last = c("Hopper"),
                 lucky_number = c(0))
df <- rbind(df, list("Marie", "Curie", 238) )
df <- cbind(df, coffeetime = c(TRUE,TRUE))
```

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

## 現実的な例

So far, you have seen the basics of manipulating data frames with our cat data;
now let's use those skills to digest a more realistic dataset. Let's read in the
`gapminder` dataset that we downloaded previously:

```{r}
gapminder <- read.csv("data/gapminder_data.csv")
```

:::::::::::::::::::::::::::::::::::::::::  callout

## いろいろなヒント

- Another type of file you might encounter are tab-separated value files (.tsv). To specify a tab as a separator, use `"\\t"` or `read.delim()`.

- Files can also be downloaded directly from the Internet into a local
  folder of your choice onto your computer using the `download.file` function.
  The `read.csv` function can then be executed to read the downloaded file from the download location, for example,

```{r, eval=FALSE, echo=TRUE}
download.file("https://raw.githubusercontent.com/swcarpentry/r-novice-gapminder/main/episodes/data/gapminder_data.csv", destfile = "data/gapminder_data.csv")
gapminder <- read.csv("data/gapminder_data.csv")
```

- Alternatively, you can also read in files directly into R from the Internet by replacing the file paths with a web address in `read.csv`. One should note that in doing this no local copy of the csv file is first saved onto your computer. 例えば：

```{r, eval=FALSE, echo=TRUE}
gapminder <- read.csv("https://raw.githubusercontent.com/swcarpentry/r-novice-gapminder/main/episodes/data/gapminder_data.csv")
```

- You can read directly from excel spreadsheets without
  converting them to plain text first by using the [readxl](https://cran.r-project.org/package=readxl) package.

- The argument "stringsAsFactors" can be useful to tell R how to read strings either as factors or as character strings. In R versions after 4.0, all strings are read-in as characters by default, but in earlier versions of R, strings are read-in as factors by default. For more information, see the call-out in [the previous episode](https://swcarpentry.github.io/r-novice-gapminder/04-data-structures-part1.html#check-your-data-for-factors).

::::::::::::::::::::::::::::::::::::::::::::::::::

gapminderを少し見てみましょう。いつも、まずしなければいけないことは、 データがどうなっているかを`str`で見てみることです：

```{r}
str(gapminder)
```

An additional method for examining the structure of gapminder is to use the `summary` function. This function can be used on various objects in R. For data frames, `summary` yields a numeric, tabular, or descriptive summary of each column. Numeric or integer columns are described by the descriptive statistics (quartiles and mean), and character columns by its length, class, and mode.

```{r}
summary(gapminder)
```

Along with the `str` and `summary` functions, we can examine individual columns of the data frame with our `typeof` function:

```{r}
typeof(gapminder$year)
typeof(gapminder$country)
str(gapminder$country)
```

データフレームの次元について見てみることもできます。 `str(gapminder)` が、gapminderには、6変数について1704の観測値があると言っていたことを念頭に置き、 以下から何が出てくると思いますか？それはなぜですか？

```{r}
length(gapminder)
```

予想としては、データフレームの長さは行数（1704）だと思うものですが、実はそうではありません。 データフレームは、 ベクトルと順序なし因子型のリストである ということを思い出しましょう：

```{r}
typeof(gapminder)
```

`length`が、6と返ってくるのは、gapminderは、6つの列のリストから成っているからです。 データセットで、行と列の数を知るためには、こうしてみましょう：

```{r}
nrow(gapminder)
ncol(gapminder)
```

または、両方を同時に：

```{r}
dim(gapminder)
```

全ての列のタイトルを知りたいと思うことも多いと思うので、後で聞いてみましょう：

```{r}
colnames(gapminder)
```

この段階で、Rが伝える構造が自分の直感や予想と合っているかを自問することが大切です。 それぞれの列の基本的なデータ型は、思った通りのデータ型になってますか？もしなっていないのなら、今後、予想外の事態を引き起こさないように、 今の時点で、問題を解決しておく必要があります。そのためには、これまでに学んだ、Rがどのようにデータを解釈するか、 そしてデータを記録する際の 厳格な整合性 の重要性といった知識を活かしましょう。

データ型と構造に満足することができたら、データを詳しく見始めることができます。 最初のいくつかの行を見てみましょう：

```{r}
head(gapminder)
```

:::::::::::::::::::::::::::::::::::::::  challenge

## チャレンジ２

It's good practice to also check the last few lines of your data and some in the middle. How would you do this?

Searching for ones specifically in the middle isn't too hard, but we could ask for a few lines at random. How would you code this?

:::::::::::::::  solution

## チャレンジ３の解答

To check the last few lines it's relatively simple as R already has a function for this:

```r
tail(gapminder)
tail(gapminder, n = 15)
```

What about a few arbitrary rows just in case something is odd in the middle?

## Tip: There are several ways to achieve this.

The solution here presents one form of using nested functions, i.e. a function passed as an argument to another function. This might sound like a new concept, but you are already using it!
Remember my\_dataframe[rows, cols] will print to screen your data frame with the number of rows and columns you asked for (although you might have asked for a range or named columns for example). How would you get the last row if you don't know how many rows your data frame has? R has a function for this. What about getting a (pseudorandom) sample? R also has a function for this.

```r
gapminder[sample(nrow(gapminder), 5), ]
```

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

分析を再現可能にするためには、後で使えるようにコードをスクリプトファイルに置く必要があります。

:::::::::::::::::::::::::::::::::::::::  challenge

## チャレンジ３

Go to file -> new file -> R script, and write an R script
to load in the gapminder dataset. Put it in the `scripts/`
directory and add it to version control.

Run the script using the `source` function, using the file path
as its argument (or by pressing the "source" button in RStudio).

:::::::::::::::  solution

## チャレンジ３の解答

The `source` function can be used to use a script within a script.
Assume you would like to load the same type of file over and over
again and therefore you need to specify the arguments to fit the
needs of your file. Instead of writing the necessary argument again
and again you could just write it once and save it as a script. Then,
you can use `source("Your_Script_containing_the_load_function")` in a new
script to use the function of that script without writing everything again.
Check out `?source` to find out more.

```{r, eval=FALSE}
download.file("https://raw.githubusercontent.com/swcarpentry/r-novice-gapminder/main/episodes/data/gapminder_data.csv", destfile = "data/gapminder_data.csv")
gapminder <- read.csv(file = "data/gapminder_data.csv")
```

To run the script and load the data into the `gapminder` variable:

```{r, eval=FALSE}
source(file = "scripts/load-gapminder.R")
```

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::  challenge

## チャレンジ４

`str(gapminder)` の結果を再び読みましょう。
今度は、順序なし因数、リスト、ベクトルについて学んだことを使いましょう。

:::::::::::::::  solution

## チャレンジ３の解答

The object `gapminder` is a data frame with columns

- `country` and `continent` are character strings.
- 理解できないところがあれば、近くの人と話し合ってみましょう。
- チャレンジ５の解答 `gapminder` というオブジェクトは、データフレームで、 - `country` と `continent` という順序なし因子型、 - `year` という整数型のベクトル、 - `pop`、 `lifeExp`、 `gdpPercap` という数値型のベクトルの行を持っています。

:::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::::::

:::::::::::::::::::::::::::::::::::::::: keypoints

- Use `cbind()` to add a new column to a data frame.
- Use `rbind()` to add a new row to a data frame.
- Remove rows from a data frame.
- Use `str()`, `summary()`, `nrow()`, `ncol()`, `dim()`, `colnames()`, `head()`, and `typeof()` to understand the structure of a data frame.
- Read in a csv file using `read.csv()`.
- Understand what `length()` of a data frame represents.

::::::::::::::::::::::::::::::::::::::::::::::::::
